### 2022-06-21 README.Rmd
Amended the template egnerotrs. No EWN.
Now incluodes checkmsedata, comparevar, and plotscene. Can now import outputs from sizemod. No EWN.

>>>>

* 2022-06-22 aMSE 0.0.7 Now have rewritecontrolfile and rewritesaudatafile and the option to include a table of parameters from sizemod into the inputs of aMSE. Have begun development of functions to aid comparing the output from different scenarios, including tables and plots. No EWN.

* 2022-06-08 aMSE 0.0.6 Have revised the ctrltemplate and datatemplate generators so that they reflect a lambda = 0.75 and correctly use the hyperstability. No EWN
